---
name: Daniel
surname: Rodr{\'{i}}guez
position: "Ph.D. Student"
address: "JMU-Wuerzburg"
email: "daniel.rodriguez@stud-mail.uni-wuerzburg.de "
orcid: 0000-0001-9637-1364
www: https://www.researchgate.net/profile/Daniel-Rodriguez-Leon
linkedin: dsrodriguezl
github: dsrodriguezl
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Biologist with a great interest in Behavioral and Chemical Ecology, in particular towards the study of Social Organization and Evolution, as well as Animal Communication."
docname: CV
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Higher Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Detail,
  "Bachelor of Science Biology", "2011-2016", "Universidad Nacional de Colombia", "Bogot{\'{a}}, Colombia", "Bachelor thesis: Variation of the relative abundance and diet of dogs (Canis lupus familiaris) on a gradient of human presence in a natural preserve of the civil society (Tabio, Cundinamarca).",
  "Master of Science Biosciences", "2017-2020", "Julius-Maximilians-Universität Würzburg", "Würzburg, Germany", "Master thesis: Variation of cuticular hydrocarbon profiles among honeybee workers from different European subspecies."
) %>% 
  detailed_entries(Degree, Year, Institution, Where, Detail)
```

# Professional experience

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Detail,
  "Bachelor of Science Biology", "2011-2016", "Universidad Nacional de Colombia", "Bogota, Colombia", "Bachelor thesis: Variation of the relative abundance and diet of dogs (Canis lupus familiaris) on a gradient of human presence in a natural preserve of the civil society (Tabio, Cundinamarca).",
  "Master of Science Biosciences", "2017-2020", "Julius-Maximilians-Universitaet Wuerzburg", "Wuerzburg, Germany", "Master thesis: Variation of cuticular hydrocarbon profiles among honeybee workers from different European subspecies."
) %>% 
  detailed_entries(Degree, Year, Institution, Where, Detail)
```

# Continuing Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~Detail,
  "Bachelor of Science Biology", "2011-2016", "Universidad Nacional de Colombia", "Bogota, Colombia", "Bachelor thesis: Variation of the relative abundance and diet of dogs (Canis lupus familiaris) on a gradient of human presence in a natural preserve of the civil society (Tabio, Cundinamarca).",
  "Master of Science Biosciences", "2017-2020", "Julius-Maximilians-Universitaet Wuerzburg", "Wuerzburg, Germany", "Master thesis: Variation of cuticular hydrocarbon profiles among honeybee workers from different European subspecies."
) %>% 
  detailed_entries(Degree, Year, Institution, Where, Detail)
```

# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

# Additional Qualifications

```{r}
tribble(
  ~Area, ~Qualification, ~Proficiency,
  "Software", "Microsoft Office (Word, Excel, PowerPoint, oneNote)", "Good knowledge (User)",
  "Software", "R", "Basic knowledge",
  "Software", "RMarkdown", "Basic knowledge",
  "Software", "Git", "Beginner",
  "Software", "Markdown", "Beginner",
  "Languages", "Spanish", "Mother tongue",
  "Languages", "English", "Advance (C1)",
  "Languages", "German", "Intermediate (B2)"
) %>% 
  brief_entries(Area, Qualification, Proficiency)
```

# Some stuff about me

 * Organized and independent in settling and conducting scientific experiments
 * Interest in interdisciplinary and intercultural research collaborations
 * Strong background in chemical ecology (i.e. GC-MS analysis)
 * Solid theoretical knowledge of behavioral ecology (e.g. Social evolution and division of labor)

