%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by
% Vel (vel@LaTeXTemplates.com)
%
% Adapted to be an Rmarkdown template by Rob J Hyndman
% 23 November 2018
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,]{twentysecondcv}

\usepackage[scaled=0.86]{DejaVuSansMono}

\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{csquotes}

\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

\usepackage{booktabs}



%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

% Profile pic
\profilepic{}

\cvname{DanielRodriguez} % Your name

\cvjobtitle{Ph.D.~Student} % Job title/career
\cvdate{April 2021} % Date of birth or date of CV??
\cvaddress{JMU-Wuerzburg} % Short address/location, use \newline if more than 1 line is required
\cvnumberphone{} % Phone number
\cvsite{\href{http://\url{https://www.researchgate.net/profile/Daniel-Rodriguez-Leon}}{\url{https://www.researchgate.net/profile/Daniel-Rodriguez-Leon}}} % Personal website
\cvmail{\href{mailto:daniel.rodriguez@stud-mail.uni-wuerzburg.de}{\nolinkurl{daniel.rodriguez@stud-mail.uni-wuerzburg.de}}} % Email address
\cvtwitter{}
\cvgithub{\href{https://github.com/dsrodriguezl}{dsrodriguezl}}
\cvlinkedin{\href{https://www.linkedin.com/in/dsrodriguezl}{dsrodriguezl}}

\lfoot{\sf CV: Daniel Rodriguez}
\rfoot{\sf\thepage}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}
\aboutme{I am a biologist with a great interest in Behavioral and
Chemical Ecology}

% Skill bar section, each skill must have a value between 0 an 6 (float)
%\skills{{pursuer of rabbits/5.8},{good manners/4},{outgoing/4.3},{polite/4},{Java/0.01}}

% Skill text section, each skill must have a value between 0 an 6
%\skillstext{{lovely/4},{narcissistic/3}}

\makeprofile % Print the sidebar




\hypertarget{higher-education}{%
\section{Higher Education}\label{higher-education}}

\nopagebreak

\begin{twenty}
    \twentyitem{2011-2016}{Bachelor of Science Biology}{Universidad Nacional de Colombia}{Bogota, Colombia\par\begin{minipage}{0.7\textwidth}%
\begin{itemize}%
\item Bachelor thesis: Variation of the relative abundance and diet of dogs (Canis lupus familiaris) on a gradient of human presence in a natural preserve of the civil society (Tabio, Cundinamarca).%
\end{itemize}%
\end{minipage}}
    \twentyitem{2017-2020}{Master of Science Biosciences}{Julius-Maximilians-Universitaet Wuerzburg}{Wuerzburg, Germany\par\begin{minipage}{0.7\textwidth}%
\begin{itemize}%
\item Master thesis: Variation of cuticular hydrocarbon profiles among honeybee workers from different European subspecies.%
\end{itemize}%
\end{minipage}}
\end{twenty}

\hypertarget{professional-experience}{%
\section{Professional experience}\label{professional-experience}}

\hypertarget{continuing-education}{%
\section{Continuing Education}\label{continuing-education}}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-RodriguezLeon2019}{}%
\CSLLeftMargin{1. }
\CSLRightInline{Rodríguez León, D. S., \& López Arévalo, H. F.
(2019). Variación de la abundancia relativa de perros en un gradiente
de presencia humana en dos reservas privadas (Tabio, Cundinamarca).
\emph{Acta Biológica Colombiana}, \emph{24}(2), 379--390.
\url{https://doi.org/10.15446/abc.v24n2.70608}}

\hypertarget{additional-qualifications}{%
\section{Additional Qualifications}\label{additional-qualifications}}

\nopagebreak

\begin{twentyshort}
    \twentyitemshort{Microsoft Office (Word, Excel, PowerPoint, oneNote)}{Software. Good knowledge (User)}
    \twentyitemshort{R}{Software. Basic knowledge}
    \twentyitemshort{RMarkdown}{Software. Basic knowledge}
    \twentyitemshort{Git}{Software. Beginner}
    \twentyitemshort{Markdown}{Software. Beginner}
    \twentyitemshort{Spanish}{Languages. Mother tongue}
    \twentyitemshort{English}{Languages. Advance (C1)}
    \twentyitemshort{German}{Languages. Intermediate (B2)}
\end{twentyshort}


\end{document}
